### 2020-08-23 thesis/thesis.tex
[thesis] Coexamples for Freak coeffects

\noindent
TODO maybe example with comparison for these two approaches could be useful here?

@@

    \begin{center}
        % TODO: a in A under prod
        {$\displaystyle {\llbracket op \rrbracket}_M : \prod_{a \in A}{|I|} \rightarrow \prod_{p \in P}{|I|} $}
    \end{center}

@@

    TODO Examples for cohandlers

>>>>

@@

    \begin{center}
        {$\displaystyle {\llbracket op \rrbracket}_M : \prod_{a \in A}{|I|} \rightarrow \prod_{p \in P}{|I|} $}
    \end{center}

@@

    TODO Introduction into coeffects from Freak side

    \subsection{File handling}

    The first example we are going to show is file handling. As per
    Section~\ref{sec:problem-statement}, we do not want to expose file handle
    to the user, thus we hide it behind carrier of FileIO coalgebraic theory,
    for which the signature is composed of Open, Write and Close operations.

\begin{verbatim}
    cohandle FileIO using "filename.txt" at
        let _ <- observe Open () in
        let _ <- observe Write "Karma Chameleon" in
        let _ <- observe Close () in
        return 42
    through {
        Open p r ->
            let filename <- return fst p in
            let fh <- do OpenBI filename in
            r (fh, ()) |
        Write p r ->
            let fh <- return fst p in
            let _ <- do WriteBI fh in
            r (fh, ()) |
        Close p r ->
            let fh <- return fst p in
            let _ <- do CloseBI fh in
            r ((), ()) |
        return x -> return x
    }
\end{verbatim}

    In the above code, we initialize the coalgebra carrier with filename that
    we want to handle, we open file, write to it once and then close it. Notice
    that file handle is not present in the user code, but only accessible in
    the runner of FileIO as a first element of a pair.

    \subsection{Nondeterministic Finite Automata}

    This example shows how one can implement NFA using coeffects. We abstract
    over internal state of the automata, and based on letters from the alphabet,
    we change automata configuration and return whether word is accepted or not.
    The code below returns whether given NFA accepts word "abba".

\begin{verbatim}
    cohandle Automata using 0 at
        let _ <- observe NFA a in
        let _ <- observe NFA b in
        let _ <- observe NFA b in
        observe NFA a
    through {
        NFA p r ->
            let state <- return fst p in
            let letter <- return snd p in
            <code transitions here> |
        return x -> return x
    }
\end{verbatim}
